---
title: "Introduction to susoflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to susoflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,  
  comment = "#>"
)
```

```{r setup, include = FALSE, echo=FALSE}
library(susoflows)
```


## Authentication

The `susoflows` packages uses the same authentication as `susoapi`. To set credentials, use `susoapi` as follows:

```{r set_credentials}
# set credentials for connecting with the server
set_credentials(
  server = "https://example.server",
  user = "My_API_user1",
  password = "MySecretPassword2Day"
)
```

Then, `susoflows` functions can use those credentials:

```{r get_logs}
# use those credentials without needing to specify them again
action_logs <- get_all_user_logs(
  start = "2021-01-01",
  end = "2021-04-01"
)
```


Alternatively, one can simply specify the `server`, `user`, and `password` parameters to any `susoflows` function.

## Usage

The `susoflows` package aims to encapsulate common or complex Survey Solutions workflows in single functions. Functions currently cover two domains:

1. Downloading
1. Monitoring

### Downloading

With a single function, one can download by questionnaire ID (`download_data`) or by questionnaire title (`download_matching`). With other single functions, one can download all types of data for one questionnaire (`download_all_data_types`) or all data types for all questionnaires (`download_all`)

If data download fails, functions will help users recover. For `download_matching`, for example, will inform the user if no matching questionnaires are found, and `find_matching_qnrs` will return matching questionnaires in order to help users refine their searches.

### Monitoring

With single function, one can also collect user action logs. With `get_all_user_logs`, one collects the logs into a data frame. With `get_last_sync_dates`, one collects the logs, parses them, and returns a data frame of the last sync dates for each interviewer.
